Evolution of solar wind discontinuities in the inner heliosphere

### 2024-02-20 index.qmd
update

Why ARTEMIS electron data and Wind ion data?

>>>>

- [x] Why ARTEMIS electron data and Wind ion data?

## 02/20/2024

{{< embed notebooks/02_psp_events.ipynb#fig-data-products >}}

{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}

{{< embed notebooks/10_results.ipynb#fig-dvl >}}

::: {.column-screen-inset layout-nrow="1"}
{{< embed notebooks/10_results.ipynb#fig-dn-dT >}}
{{< embed notebooks/10_results.ipynb#fig-dT-dB >}}
{{< embed notebooks/10_results.ipynb#fig-dn-dB >}}
:::
